%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Goodjob - Job Connection System} $|$ \emph{Team size: 5}}    {10/2024 - 12/2024}
    \resumeItemListStart
        \resumeItem {\textbf{Description:} This project is for the Software Engineering Capstone course, where our team developed a platform for job posting and application across various industries and locations (similar to VietnamWorks, ITviec, TopDev, etc.).}
        \resumeItem {\textbf{Technologies used:} Java, Spring Boot, Restful API, Spring Data JPA, Spring Security, JWT, Spring Profiles, PostgreSQL, Railway, AWS Deployment.}
            \vspace{0.1cm}
        \resumeItem{\textbf{Role:} Technical Leader \& Backend Developer - Led the selection of the technology stack, designed system architecture and database schema, deployed the database online, developed core backend functionalities and APIs, and analyzed user requirements to create use case diagrams.}
            \vspace{0.1cm}
        \resumeItem{\textbf{Core functionalities:}}
            \resumeItemListStart
                \resumeItem{Supports four roles: admin, company, applicant, and guest, each with distinct permissions and functionalities.}
                \resumeItem{User authentication with login, registration for applicant and company roles, and role-based access control.}
                \resumeItem{Search for job posts (15 fields), companies (7 fields), and by address with hierarchical filtering (province to ward)}
                \resumeItem{User profile management: view, edit (with role-dependent fields), delete, change password, view notifications.}
                \resumeItem{Company rating with stars, adjusted based on user feedback.}
                \resumeItem{Notifications for company ratings, application submissions, and status updates.}
                \resumeItem{Company functionalities: view all posted job posts; post, edit, and delete job posts; view all applications for a job post and modify application status to notify applicants; view applicant profiles; etc.}
                \resumeItem{Applicant functionalities: view job posts; apply for jobs; view all applications with status; edit or delete applications; view company profiles; rate companies with stars and feedback; mark jobs of interest to save; view saved job posts; etc.}
            \resumeItemListEnd
            \vspace{0.1cm}
            \resumeItem{\textbf{Demo:} \href{https://www.youtube.com/watch?v=-fozVZbGKv8}{\underline{youtube.com/watch?v=-fozVZbGKv8}}}

            \resumeItem{\textbf{Github repository:}   \href{https://github.com/dinhduc0794/job-connection-system-co3103}{\underline{github.com/dinhduc0794/job-connection-system-co3103}}}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Real Estate Rental Management System} $|$ \emph{Personal Project}}    {8/2024 - 12/2024}
    \resumeItemListStart
        \resumeItem {\textbf{Description:} This personal project aims to deepen my understanding of web backend development using Java, with progress documented through commits across multiple branches of my GitHub repository.}
        \resumeItem {\textbf{Technologies used:} }
        \resumeItemListStart
            \resumeItem{Backend: Java, Spring MVC, JPA, Spring Data JPA, Spring Security, JWT, Spring Profiles, MySQL, Kafka etc.}
            \resumeItem{Frontend: HTML5, CSS3, JavaScript, Bootstrap, JQuery, Ajax.}
        \resumeItemListEnd
        \vspace{0.1cm}
        \resumeItem{\textbf{Core functionalities:}}
        \resumeItemListStart
            \resumeItem{User authentication and authorization (login, registration, role-based access control).}
            \resumeItem{Search for buildings (16 fields), customers (6 fields), accounts (2 fields), ensuring secure access to relevant data.}
            \resumeItem{CRUD operations for managing buildings, customers, and user accounts.}
            \resumeItem{Assigned buildings to management staff.}
            \resumeItem{Managed multiple transactions between customers and staff.}
            \resumeItem{Enabled customers to leave contact information for inquiries or consultation.}
        \resumeItemListEnd
        \vspace{0.1cm}
        \resumeItem{\textbf{Github repository:}   \href{https://github.com/dinhduc0794/real-estate-rental-mgmt}{\underline{github.com/dinhduc0794/real-estate-rental-mgmt}}}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Examify - Online Examination System} $|$ \emph{Team size: 9 (1 Product Owner, 1 Scrum Master, 7 Developer)}}    {3/2025}
    \resumeItemListStart
        \resumeItem {\textbf{Description:} 
        Completed a Scrum course by Axon Active and HCMUT, focusing on Agile Scrum methodologies as part of the Advanced Software Engineering curriculum. I worked on a 2-day project (3 sprints, each approximately 4 hours). Examify - Online Examination System is a webapp platform designed to support teachers in conducting online assessments (similar to Azota, Quizizz, or Kahoot).}
        \resumeItem {\textbf{Technologies used:} Java, Spring Boot, Spring Security, JWT, PostgreSQL, Azure (deployment), Trello (project management), Notion (API documentation).}
        \resumeItem{\textbf{Role:} Scrum Master \& Backend Developer - Facilitated Agile Scrum processes (sprint planning, daily stand-ups, retrospectives) for a 9-member team and contributed to the implementation of 25+ RESTful APIs for the system.}
        \resumeItem{\textbf{Core functionalities:} Teachers create and manage tests, while students access them using a passcode and submit answers online. Results are tracked for each student and test, with teachers able to analyze class performance. User authentication is role-based (teacher, student).}
        \vspace{0.1cm}
        \resumeItem{\textbf{Deployed website:} \href{https://examify-online.azurewebsites.net}{\underline{examify-online.azurewebsites.net}}}
        \resumeItem{\textbf{GitHub repositories:}}
        \resumeItemListStart
            \resumeItem{Backend: \href{https://github.com/ABsievil/BE_Examify-System}{\underline{github.com/ABsievil/BE\_Examify-System}}}
            \resumeItem{Frontend: \href{https://github.com/Gloxiniaaa/Examify-FE}{\underline{github.com/Gloxiniaaa/Examify-FE}}}
        \resumeItemListEnd
        \vspace{0.1cm}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Student Smart Printing Service for HCMUT} $|$ \emph{Team size: 7}}    {10/2024 - 12/2024}
    \resumeItemListStart
        \resumeItem {\textbf{Description:} This project is for the Software Engineering course, where our team developed a system for automatic printing scheduling for students at the Ho Chi Minh City University of Technology.}
        \resumeItem {\textbf{Technologies used:} Java, Spring Boot, Restful API, Spring Data JPA, Spring Security, JWT, Spring Profiles, PostgreSQL, Aiven.}
        \vspace{0.1cm}
        \resumeItem{\textbf{Role:} Leader \& Backend Developer - Determined the technology stack, individually developed core backend functionalities and APIs, designed system architecture, activity \& component diagrams, deployed the database.}
        \vspace{0.1cm}
        \resumeItem{\textbf{Core functionalities:}}
        \resumeItemListStart
            \resumeItem{User authentication and authorization (login, registration, role-based access control).}
            \resumeItem{Students can initiate the printing process (schedule printing, select available printer, upload documents, configure print settings, and add paper if needed).}
            \resumeItem{Students can purchase additional paper for printing.}
            \resumeItem{Students can view their printing logs and paper purchase logs.}
        \resumeItemListEnd
        \vspace{0.1cm}
        \resumeItem{\textbf{Github repository:}   \href{https://github.com/dinhduc0794/student-smart-printing-service_co3001}{\underline{github.com/dinhduc0794/student-smart-printing-service-co3001}}}
    \resumeItemListEnd

    % \resumeProjectHeading
    % {\textbf{Bach Khoa LMS - Learning Management System} $|$ \emph{Team size: 7}}    {4/2024 - 5/2024}
    % \resumeItemListStart
    %     \resumeItem {\textbf{Description:} 
    %     Developed an LMS based on the BK E-Learning platform for our Advanced Programming Course, including features such as course registration, viewing course details, file uploads, quizzes, and role-based access control for comprehensive course management and interactive learning.}
    %     \resumeItem {\textbf{Technologies used:} Spring Boot, Spring Security, JWT, Bootstrap, Google Firebase.}
    %     \resumeItem{\textbf{Role:} Frontend Developer – Built the UI for the homepage, login page, registration page, my-courses page, course registration/deregistration, course details, learning progress, class list, and quiz page using pure HTML5, CSS3, and JavaScript without any frameworks or libraries.}
    %     \resumeItem{\textbf{Demo:}   \href{https://drive.google.com/file/d/11JahlbTDULiIy2puol8M3Zlyh3SxRBOJ/view?usp=sharing}{\underline{LMS\_AdvancedProgramming.mp4}}}
    % \resumeItemListEnd
\resumeSubHeadingListEnd
